Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-01-15 apples_and_oranges.qmd

# for cdrs only
cdrs_study_ids <- df_with_distinct_instruments %>%
  filter(instrument_name == "cdrs")) %>%
  pull(new_study_id)
df_with_distinct_instruments <- df_with_distinct_instruments %>%
  mutate(key4 = ifelse(new_study_id %in% cdrs_study_ids, 4, NA))

@@

>>>>

# for cdrs only
cdrs_study_ids <- df_with_distinct_instruments %>%
  filter(instrument_name == "cdrs") %>%
  pull(new_study_id)
df_with_distinct_instruments <- df_with_distinct_instruments %>%
  mutate(key4 = ifelse(new_study_id %in% cdrs_study_ids, 4, NA))

@@

We have also run models to take into accountregression to the mean within CDRS and HAMD.

```{r, warning=FALSE, message = FALSE, echo=FALSE}
####code to extract baseline-adjusted post means for CDRS and HAMD

de_meaned_baselilne_mean_cdrs <- (list_cdrs_study[[1]]$baseline_mean - mean(list_cdrs_study[[1]]$baseline_mean, na.rm = TRUE))

lm_for_cdrs_smds <- lm(list_cdrs_study[[1]]$post_mean ~ de_meaned_baselilne_mean_cdrs +list_cdrs_study[[1]]$four_level_var,

  na.action=na.exclude,

   )

#summary(lm_for_cdrs_smds)

coefs_lm_for_cdrs_smds  <- broom:: tidy(lm_for_cdrs_smds)

condition <- coefs_lm_for_cdrs_smds$term

cdrs_smds <-c(coefs_lm_for_cdrs_smds$estimate[1], coefs_lm_for_cdrs_smds$estimate[-1] + coefs_lm_for_cdrs_smds$estimate[1])

cdrs_upper_ci <- cdrs_smds + coefs_lm_for_cdrs_smds$std.error*1.96

cdrs_lower_ci <- cdrs_smds - coefs_lm_for_cdrs_smds$std.error*1.96

cdrs_smd_with_cis <- data.frame (

  condition = levels(list_hamd_study$four_level_var),

  cdrs_smds = cdrs_smds[-2],

  cdrs_upper_ci = cdrs_upper_ci[-2],

  cdrs_lower_ci = cdrs_lower_ci[-2]

)

# do the same for hamd

de_meaned_baselilne_mean_hamd <- (list_hamd_study$baseline_mean - mean(list_hamd_study$baseline_mean, na.rm = TRUE))

lm_for_hamd_smds <- lm(list_hamd_study$post_mean ~ de_meaned_baselilne_mean_hamd +list_hamd_study$four_level_var,

                       na.action=na.exclude,

)

#summary(lm_for_hamd_smds)

coefs_lm_for_hamd_smds  <- broom:: tidy(lm_for_hamd_smds)

condition <- coefs_lm_for_hamd_smds$term

hamd_smds <-c(coefs_lm_for_hamd_smds$estimate[1], coefs_lm_for_hamd_smds$estimate[-1] + coefs_lm_for_hamd_smds$estimate[1])

hamd_upper_ci <- hamd_smds + coefs_lm_for_hamd_smds$std.error*1.96

hamd_lower_ci <- hamd_smds - coefs_lm_for_hamd_smds$std.error*1.96

hamd_smd_with_cis <- data.frame (

condition = levels(list_hamd_study$four_level_var),

hamd_smds = hamd_smds[-2],

hamd_upper_ci = hamd_upper_ci[-2],

hamd_lower_ci = hamd_lower_ci[-2]

)

Tables 6a and 6b show the baeline-mean adjusted SMDs for the CDRS at outcome when the baseline measurement has been taken into account. <!--# Here Intercept refers to teh psychotherapy control. Sorry about the labelling of the rows, will improve. -->

```{r}
knitr:: kable(cdrs_smd_with_cis, caption = "Table 6a. CDRS baseline mean adjsuted SMDs")
```

```{r, warning=FALSE, message = FALSE, echo=FALSE}
knitr:: kable(hamd_smd_with_cis, caption = "Table 6. HAM-D baseline-mean adjusted SMDs")
```
